DeepAutoTrack (DAC): Car Trajectory Prediction for Autonomous Driving

### 2017-11-11 paper/cvpr2018/cvpr2018_draft.tex
latex paper writing

\documentclass[10pt,twocolumn,letterpaper]{article}
 \pdfoutput=1
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{subcaption}
\usepackage{slashbox}
\usepackage{color}
\usepackage[english]{babel}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

@@

\author{Di Wu, Zhennan Wang, Yi Tang,  Wenbin Zou, Xia Li\\
Shenzhen University\thanks{Shenzhen Key Lab of Advanced Telecommunication and Information Processing, College of Information Engineering, Shenzhen University.}\\
{\tt\small dwu,...@szu.edu.cn}}
\maketitle
%%%%%%%%% ABSTRACT
\begin{abstract}

\end{abstract}
%%%%%%%%% BODY TEXT
%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/
%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
%%% https://cs.stanford.edu/people/widom/paper-writing.html
\section{Introduction}

@@

\textbf{\emph{3. Why is it hard? (E.g., why do naive approaches fail?)}}

@@

@@

Currently, most public datasets with semantic labelling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
We collect car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map.

Scene diversity: European style town, modern city, highway and green areas
Variety of dynamic objects: cars, pedestrians and cyclists

Multiple seasons: dedicated themes for winter, fall, spring and summer

Lighting conditions and weather: dynamic lights and shadows, several day-time modes, rain mode and night mode

Automatic groundtruth: individual instances for semantic segmentation (pixelwise annotations), depth, car ego-motion
 of photo-realistic frames rendered from a virtual city and comes with precise pixel-level semantic annonations for 13 classes, \emph{i.e.}: miscellaneous, sky, building, road, sidewalk, fence, vegetation, pole, car, sign, pedestrian, cyclist, lanemarking.

The focus of this paper is on car trajectory prediction on high ways. In the SYNTHIA

Some sample frames with its sementic labels and depth information is shown in Fig. (TODO: TY help to generate the figures).
\subsection{traffic participants detection}

@@

@@

@@

\section{Conclusions}

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}
 \pdfoutput=1
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
%\usepackage{subcaption}
%\usepackage{slashbox}
\usepackage{color}
\usepackage[english]{babel}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

@@

\author{Di Wu, Zhennan Wang, Yi Tang,  Wenbin Zou, Xia Li\\
Shenzhen University\thanks{Shenzhen Key Lab of Advanced Telecommunication and Information Processing, College of Information Engineering, Shenzhen University.}\\
{\tt\small dwu,...@szu.edu.cn}}
\maketitle
%%%%%%%%% ABSTRACT
\begin{abstract}
TODO: abstract
This guide is patterned after my “Doing well in your courses”, a post I wrote a long time ago on some of the tips/tricks I’ve developed during my undergrad. I’ve received nice comments about that guide, so in the same spirit, now that my PhD has come to an end I wanted to compile a similar retrospective document in hopes that it might be helpful to some. Unlike the undergraduate guide, this one was much more difficult to write because there is significantly more variation in how one can traverse the PhD experience. Therefore, many things are likely contentious and a good fraction will be specific to what I’m familiar with (Computer Science / Machine Learning / Computer Vision research). But disclaimers are boring, lets get to it!
\end{abstract}
%%%%%%%%% BODY TEXT
%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/
%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
%%% https://cs.stanford.edu/people/widom/paper-writing.html
\section{Introduction}

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ {\small TODO: Pull figure caption goes here.}}
        \label{fig:response_map}
\end{figure}
\textbf{\emph{3. Why is it hard? (E.g., why do naive approaches fail?)}}

@@

~\cite{xu2017end}: End-to-end learning of driving models from large-scale video dataset.

~\cite{behl2017bounding} Bounding Boxes, Segmentations and Object Coordinates: How Important is Recognition for 3D Scene Flow Estimation in Autonomous Driving Scenarios?

~\cite{chen2015deepdriving} DeepDriving: Learning Affordance for Direct Perception

~\cite{kim2017interpretable} Interpretable Learning for Self-driving cars

@@

Currently, most public datasets with semantic labelling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
We collect car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
The potential of this virtual world includes extension capabilities: new parts of the cities and road conditions can be easily generated by adding different setups. The major features of collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).

There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map. In our experiment, we used only left front camera view data.
The focus of this paper is on car trajectory prediction on high ways. We list our logic for collecting continuous car tracking in List~\ref{Dataset_collection}. (TODO: make a list).
Some sample frames with its sementic labels and depth information is shown in Fig. (TODO: TY help to generate the figures).

\begin{algorithm}
\caption{Multimodal Deep Dynamic Networks -- training}\label{Dataset_collection}
\LinesNumbered
\SetAlgoLined
\SetAlgoNoEnd
\DontPrintSemicolon
\SetKwFunction{zeroes}{zeroes}
\KwData{\;
          $ \mathbf{X^1=\{ x^1_i\}_{i \in [1 \ldots t]}}$ - raw input(skeletal) feature sequence.\;
          $ \mathbf{X^2=\{ x^2_i\}_{i \in [1 \ldots t]}}$ - raw input(depth) feature sequence in the form of \;
          \hspace{1cm}$M_1 \times M_2 \times T$, where $M_1, M_2$ are the height and width of the input \;
          \hspace{1cm}  image and $T$ is the number of contiguous frames of the \;
          \hspace{1cm} spatio-temporal cuboid. \;
          \hspace{1cm}  {\scriptsize{}Note that the GPU library \emph{cuda-convnet}~\cite{krizhevsky2012imagenet} used requires square size images and $T$ is a multiple of $4$}.\;
          $ \mathbf{Y=\{ y_i\}_{i \in [1 \ldots t]}}$  - frame based local label (achieved by semi-supervised \; \hspace{1cm} forced-aligment), \;
          \hspace{1cm}  where $ \mathbf{y_i} \in \{ C * S + \textbf{\emph{1}} \} $ with $C$ is the number of class, $S$ is the  \;
          \hspace{1cm}  number of hidden states for each class, $\textbf{\emph{1}}$ as ergodic state.
            }
\For{$m \leftarrow 1$ to $2$}{
    \SetAlgoVlined
    \eIf{$m$ is $1$}{
        Preprocessing the dataCordts2016Cityscapes $ \mathbf{X^1}$ as in Eq.\ref{sk_features}.\;
        Normalizing(zero mean, unit variance per dimension) the above features and feed to to Eq.\ref{GRBMenergy}. \;
        Pre-training the networks using \emph{Contrastive Divergence}. \;
        Supervised fine-tuning the Deep Belief Networks using $ \mathbf{Y}$ by standard mini-batch \emph{SGD} backpropagation.\;
    }{
        Preprocessing the data $ \mathbf{X^2}$ (normalizing, median filtering the depth data) Algo.\ref{normalization_scheme_1} or Algo.\ref{normalization_scheme_2}.\;
        Feeding the above features to Eq.\ref{ReLU}. \;
        Supervised fine-tuning the Deep 3D Convolutional Neural Networks using $ \mathbf{Y}$ by standard mini-batch \emph{SGD} Backpropagation.\;
    }
}
\KwResult{\;
        $\mathbf{GDBN}$ - a gaussian bernoulli visible layer Deep Belief Network to \;
                \hspace{1cm} generate the emission probabilities for hidden markov model.\;
        $\mathbf{3DCNN}$ - a 3D Deep Convolutional Neural Networks to generate the\;
                \hspace{1cm}   emission probabilities for hidden markov model.\;
        $\mathbf{p(H_1)}$ - prior probability for $ \mathbf{Y}$.\;
        $ \mathbf{p(H_t | H_{t-1})}$ - transition probability for $ \mathbf{Y}$,  enforcing the beginning and \;
                    \hspace{1cm} ending of a sequence can only start from the first or the last state.
}
\end{algorithm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Implementations}

\subsubsection{Traffic participants detection}

@@

\subsubsection{Instance tracking}

@@

\subsubsection{Trajectory prediction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evaluation}

\begin{table}[t]
\small
   \centering
        \begin{tabular}{|l|| *{2}{c}| *{2}{c} |}\hline
            {\small Configuration} & \multicolumn{2}{|c|}{\small 2D}  & \multicolumn{2}{|c|}{\small 3D}  \\ \hline \hline
                                                    & P20       & AUC       & P20       & AUC  \\ \hline \hline

            {\small MTM }                          &  58.0     &  38.4     & 64.3      & 44.0   \\
            \hline
            {\small \textbf{MTFC} }  &  66.2 ${\color{red}(8.2\uparrow)}$    &  46.1 ${\color{red}(7.7\uparrow)}$    &  71.4 ${\color{red}(7.1\uparrow)}$     &  49.1 ${\color{red}(5.1\uparrow)}$\\
            \hline
            \hline
            {\small MaxRes }                        &  57.5     &  38.8     &  65.8     &  45.9  \\
            \hline
            {\small \textbf{MTM (GT)} }        &  70.6${\color{red}(13.1\uparrow)}$     &  46.7  ${\color{red}(7.9\uparrow)}$   &  77.8 ${\color{red}(12.0\uparrow)}$    &  53.6 ${\color{red}(7.7\uparrow)}$ \\
            \hline
            \hline
            {\small \textbf{MTFC}}           &  74.0${\color{red}(3.4\uparrow)}$      &  51.8${\color{red}(5.1\uparrow)}$      &  79.8${\color{red}(2.0\uparrow)}$      &  57.0${\color{red}(3.4\uparrow)}$    \\
            \hline
            {\small \textbf{DAC}}&  74.2 ${\color{red}(0.2\uparrow)}$    &  52.1${\color{red}(0.3\uparrow)}$     &  79.9${\color{red}(0.1\uparrow)}$     &  57.4${\color{red}(0.4\uparrow)}$\\\hline

        \end{tabular}

    \caption{ {\small
          Baseline comparisons with arrows indicating performance changes comparing with the upper row parallel experiment.
          First two rows investigate the impact of projecting deep features into a kernel space \emph{vs.} using linear deep features.
          Next two rows compare the traditional using max location \emph{vs.} the proposed multi-resolution convnets paradigm for decoding target translational movement.
          Last two rows illustrate the benefit of adaptive learning rate through time (with scale update). }
          } \label{table_baseline}
\end{table}

\begin{table}[t]
\small
   \centering
        \begin{tabular}{|l|| *{2}{c}|}\hline
            {\small Configuration} & \multicolumn{2}{|c|}{\small 2D}    \\ \hline \hline
                                                  & P20       & AUC   \\ \hline \hline

            {\small MTM }                          &  58.0     &  38.4      \\
            \hline
            {\small \textbf{MTFC} }  &  66.2 ${\color{red}(8.2\uparrow)}$    &  46.1 ${\color{red}(7.7\uparrow)}$  \\
            \hline
            \hline
            {\small MaxRes }                        &  57.5     &  38.8   \\
            \hline
            {\small \textbf{MTM (GT)} }        &  70.6${\color{red}(13.1\uparrow)}$     &  46.7  ${\color{red}(7.9\uparrow)}$   \\
            \hline
            \hline
            {\small \textbf{MTFC}}           &  74.0${\color{red}(3.4\uparrow)}$      &  51.8${\color{red}(5.1\uparrow)}$     \\
            \hline
            {\small \textbf{DAC}}&  74.2 ${\color{red}(0.2\uparrow)}$    &  52.1${\color{red}(0.3\uparrow)}$    \\\hline

        \end{tabular}

    \caption{ {\small
          Comparison with the most recent methods }
          } \label{table_baseline2}
\end{table}
\section{Conclusions}
